---
title: "The Non-Linear Dynamics of Export Complexity: A Global Panel Analysis of the Interaction Between Human Capital Accumulation and Institutional Quality (1990-.......)"
author: "Michelle Aipime"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
fontsize: 12pt
geometry: "a4paper, margin=1in"
abstract: |
  ABSTRACT
  
  (Since you are building the HCT Nexus platform, this is where you will summarize how human capital accumulation and institutional quality—drawing from Acemoglu and North—drive export sophistication.)
bibliography: references.bib
link-citations: true
---

# Introduction
INTRO

# Literature Review
LITERATURE REVIEW

(Here you can integrate your HCT Nexus theories, such as the Heckscher-Ohlin Model and Endogenous Growth Theory.)

# Methodology
METHODOLOGY

# Analysis and Results
ANALYSIS AND RESULTS

# Conclusion and Recommendations
CONCLUSION AND RECOMMENDATIONS

# References

You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
